---
title: "Directed Acyclic Graphs"
author: "Lucas Puebla"
---
# Assignment 1
```{r}
# Load packages
library(tidyverse)
library(dagitty)
library(ggdag)
library(ggthemr)
ggthemr("flat")
rm(list = ls())

# Collider
collider <- dagify(
  Sales ~ Parking,
  Sales ~ Location,
  coords = list(x = c(Location = 3, Sales = 2, Parking = 1),
                y = c(Location = 1, Sales = 0, Parking = 1))
)

# Plot DAG
ggdag(collider) +
  geom_dag_point(color = ggthemr::swatch()[2]) +
  geom_dag_text(color = "white") +
  geom_dag_edges(edge_color = "white")
```


# Assignment 2
## 'satisfaction' on 'follow_ups'

```{r}
# Load data
data <- readRDS("~/GitHub/cdsba-lucaspuebla93/Causal_Data_Science_Data/customer_sat.rds")
# print(data)

# Run linear regression: satisfaction on follow_ups
model_1 <- lm(satisfaction ~ follow_ups, data = data)

# Summarize the regression results
summary(model_1)
```


## 'satisfaction' on 'follow_ups' accounting for 'subscription'

```{r}
# Run linear regression: satisfaction on follow_ups and account for subscription
model_2 <- lm(satisfaction ~ follow_ups + subscription, data = data)

# Summarize the regression results
summary(model_2)
```


# Assignment 3
The increase in the R-squared coefficient between the model not accounting and the model accounting for 'subscription' suggests that the relationship between 'follow_ups' and 'satisfaction' might vary across different subscription levels. This can be seen in the plots below. 
This difference in the 'follow_ups'-'satisfaction' relationship might be due to clients from different subscription levels having different service expectations or being more demanding regarding follow-up support. Clients subscribing to different levels might also use various features differently, impacting their need for follow-ups as well as their overall satisfaction.


# Assignment 4

```{r}
# Not conditioning on subscription
not_cond_plot <- ggplot(data, aes(x = follow_ups, y = satisfaction)) +
  geom_point() +
  stat_smooth(method = "lm", se = FALSE)

# Conditioning on subscription
cond_plot <- ggplot(data, aes(x = follow_ups, y = satisfaction,
                              color = subscription, 
                              alpha = subscription)) +
  geom_point() +
  stat_smooth(method = "lm", se = FALSE) +
  scale_color_manual(values = c("Premium" = "blue", "Premium+" = "red", "Elite" = "green")) +
  scale_alpha_manual(values = c("Premium" = 0.5, "Premium+" = 0.6, "Elite" = 0.3)) +
  theme(legend.position = "top")

# Plot both
not_cond_plot
cond_plot
```

